---
title: "Functional Classification"
author: "Aarón García Blázquez"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r dirs, echo=FALSE}
dir_docs <- "~/zebraheart-development/01-documentation/"
dir_src <- "~/zebraheart-development/02-scripts/"
dir_data <- "~/zebraheart-development/03-data/"
dir_output <- "~/zebraheart-development/04-output/"
```

```{r go_terms}
ont1 <- "GO:0007507 (Heart development)"
heart_development <- read.table(file = paste0(dir_docs,
                                              "heart_development.txt"))

ont2 <- "GO:0003015 (Cardiac contraction)"
cardiac_contraction <- read.table(file = paste0(dir_docs,
                                                "cardiac_contraction.txt"))

ont3 <- "GO:0006816 (Calcium transport)"
calcium_transport <- read.table(file = paste0(dir_docs,
                                              "calcium_transport.txt"))
```

---

# {.tabset}

## Zebrafish {.tabset}

### Own Gene Universe {.tabset}

#### 72 hpf vs 48 hpf

```{r}
load(paste0(dir_output,
            "gene_set_enrichment_analysis/",
            "TMM_GSEA_OG_GOBP_72_48.RData"))

sig_terms <- gsea_GO_OG@result[gsea_GO_OG@result$p.adjust < 0.05, ]
```

```{r}
dev_terms <- sig_terms$ID %in% heart_development$V1

n_terms <- length(which(dev_terms == TRUE))

if (n_terms == 0) {
  print(paste0("There are no significant terms related to ", ont1))
} else if (n_terms == 1) {
  print(paste0("There is ", n_terms, " significant term related to ", ont1))
} else {
  print(paste0("There are ", n_terms, " significant terms related to ", ont1))
}
```

```{r}
dev_terms <- sig_terms$ID %in% cardiac_contraction$V1

n_terms <- length(which(dev_terms == TRUE))

if (n_terms == 0) {
  print(paste0("There are no significant terms related to ", ont2))
} else if (n_terms == 1) {
  print(paste0("There is ", n_terms, " significant term related to ", ont2))
} else {
  print(paste0("There are ", n_terms, " significant terms related to ", ont2))
}
```

```{r}
dev_terms <- sig_terms$ID %in% calcium_transport$V1

n_terms <- length(which(dev_terms == TRUE))

if (n_terms == 0) {
  print(paste0("There are no significant terms related to ", ont3))
} else if (n_terms == 1) {
  print(paste0("There is ", n_terms, " significant term related to ", ont3))
} else {
  print(paste0("There are ", n_terms, " significant terms related to ", ont3))
}
```

#### 120 hpf vs 72 hpf

```{r}
load(paste0(dir_output,
            "gene_set_enrichment_analysis/",
            "TMM_GSEA_OG_GOBP_120_72.RData"))

sig_terms <- gsea_GO_OG@result[gsea_GO_OG@result$p.adjust < 0.05, ]
```

```{r}
dev_terms <- sig_terms$ID %in% heart_development$V1

n_terms <- length(which(dev_terms == TRUE))

if (n_terms == 0) {
  print(paste0("There are no significant terms related to ", ont1))
} else if (n_terms == 1) {
  print(paste0("There is ", n_terms, " significant term related to ", ont1))
} else {
  print(paste0("There are ", n_terms, " significant terms related to ", ont1))
}
```

```{r}
dev_terms <- sig_terms$ID %in% cardiac_contraction$V1

n_terms <- length(which(dev_terms == TRUE))

if (n_terms == 0) {
  print(paste0("There are no significant terms related to ", ont2))
} else if (n_terms == 1) {
  print(paste0("There is ", n_terms, " significant term related to ", ont2))
} else {
  print(paste0("There are ", n_terms, " significant terms related to ", ont2))
}
```

```{r}
dev_terms <- sig_terms$ID %in% calcium_transport$V1

n_terms <- length(which(dev_terms == TRUE))

if (n_terms == 0) {
  print(paste0("There are no significant terms related to ", ont3))
} else if (n_terms == 1) {
  print(paste0("There is ", n_terms, " significant term related to ", ont3))
} else {
  print(paste0("There are ", n_terms, " significant terms related to ", ont3))
}
```

#### Adults vs 120 hpf

```{r}
load(paste0(dir_output,
            "gene_set_enrichment_analysis/",
            "TMM_GSEA_OG_GOBP_adult_120.RData"))

sig_terms <- gsea_GO_OG@result[gsea_GO_OG@result$p.adjust < 0.05, ]
```

```{r}
dev_terms <- sig_terms$ID %in% heart_development$V1

n_terms <- length(which(dev_terms == TRUE))

if (n_terms == 0) {
  print(paste0("There are no significant terms related to ", ont1))
} else if (n_terms == 1) {
  print(paste0("There is ", n_terms, " significant term related to ", ont1))
} else {
  print(paste0("There are ", n_terms, " significant terms related to ", ont1))
}
```

```{r}
dev_terms <- sig_terms$ID %in% cardiac_contraction$V1

n_terms <- length(which(dev_terms == TRUE))

if (n_terms == 0) {
  print(paste0("There are no significant terms related to ", ont2))
} else if (n_terms == 1) {
  print(paste0("There is ", n_terms, " significant term related to ", ont2))
} else {
  print(paste0("There are ", n_terms, " significant terms related to ", ont2))
}
```

```{r}
dev_terms <- sig_terms$ID %in% calcium_transport$V1

n_terms <- length(which(dev_terms == TRUE))

if (n_terms == 0) {
  print(paste0("There are no significant terms related to ", ont3))
} else if (n_terms == 1) {
  print(paste0("There is ", n_terms, " significant term related to ", ont3))
} else {
  print(paste0("There are ", n_terms, " significant terms related to ", ont3))
}
```

### Db Package Universe {.tabset}

#### 72 hpf vs 48 hpf

```{r}
load(paste0(dir_output,
            "gene_set_enrichment_analysis/",
            "TMM_GSEA_DB_GOBP_72_48.RData"))

sig_terms <- gsea_GO_DB@result[gsea_GO_DB@result$p.adjust < 0.05, ]
```

```{r}
dev_terms <- sig_terms$ID %in% heart_development$V1

n_terms <- length(which(dev_terms == TRUE))

if (n_terms == 0) {
  print(paste0("There are no significant terms related to ", ont1))
} else if (n_terms == 1) {
  print(paste0("There is ", n_terms, " significant term related to ", ont1))
} else {
  print(paste0("There are ", n_terms, " significant terms related to ", ont1))
}
```

```{r}
dev_terms <- sig_terms$ID %in% cardiac_contraction$V1

n_terms <- length(which(dev_terms == TRUE))

if (n_terms == 0) {
  print(paste0("There are no significant terms related to ", ont2))
} else if (n_terms == 1) {
  print(paste0("There is ", n_terms, " significant term related to ", ont2))
} else {
  print(paste0("There are ", n_terms, " significant terms related to ", ont2))
}
```

```{r}
dev_terms <- sig_terms$ID %in% calcium_transport$V1

n_terms <- length(which(dev_terms == TRUE))

if (n_terms == 0) {
  print(paste0("There are no significant terms related to ", ont3))
} else if (n_terms == 1) {
  print(paste0("There is ", n_terms, " significant term related to ", ont3))
} else {
  print(paste0("There are ", n_terms, " significant terms related to ", ont3))
}
```

#### 120 hpf vs 72 hpf

```{r}
load(paste0(dir_output,
            "gene_set_enrichment_analysis/",
            "TMM_GSEA_DB_GOBP_120_72.RData"))

sig_terms <- gsea_GO_DB@result[gsea_GO_DB@result$p.adjust < 0.05, ]
```

```{r}
dev_terms <- sig_terms$ID %in% heart_development$V1

n_terms <- length(which(dev_terms == TRUE))

if (n_terms == 0) {
  print(paste0("There are no significant terms related to ", ont1))
} else if (n_terms == 1) {
  print(paste0("There is ", n_terms, " significant term related to ", ont1))
} else {
  print(paste0("There are ", n_terms, " significant terms related to ", ont1))
}
```

```{r}
dev_terms <- sig_terms$ID %in% cardiac_contraction$V1

n_terms <- length(which(dev_terms == TRUE))

if (n_terms == 0) {
  print(paste0("There are no significant terms related to ", ont2))
} else if (n_terms == 1) {
  print(paste0("There is ", n_terms, " significant term related to ", ont2))
} else {
  print(paste0("There are ", n_terms, " significant terms related to ", ont2))
}
```

```{r}
dev_terms <- sig_terms$ID %in% calcium_transport$V1

n_terms <- length(which(dev_terms == TRUE))

if (n_terms == 0) {
  print(paste0("There are no significant terms related to ", ont3))
} else if (n_terms == 1) {
  print(paste0("There is ", n_terms, " significant term related to ", ont3))
} else {
  print(paste0("There are ", n_terms, " significant terms related to ", ont3))
}
```

#### Adults vs 120 hpf

```{r}
load(paste0(dir_output,
            "gene_set_enrichment_analysis/",
            "TMM_GSEA_DB_GOBP_adult_120.RData"))

sig_terms <- gsea_GO_DB@result[gsea_GO_DB@result$p.adjust < 0.05, ]
```

```{r}
dev_terms <- sig_terms$ID %in% heart_development$V1

n_terms <- length(which(dev_terms == TRUE))

if (n_terms == 0) {
  print(paste0("There are no significant terms related to ", ont1))
} else if (n_terms == 1) {
  print(paste0("There is ", n_terms, " significant term related to ", ont1))
} else {
  print(paste0("There are ", n_terms, " significant terms related to ", ont1))
}
```

```{r}
dev_terms <- sig_terms$ID %in% cardiac_contraction$V1

n_terms <- length(which(dev_terms == TRUE))

if (n_terms == 0) {
  print(paste0("There are no significant terms related to ", ont2))
} else if (n_terms == 1) {
  print(paste0("There is ", n_terms, " significant term related to ", ont2))
} else {
  print(paste0("There are ", n_terms, " significant terms related to ", ont2))
}
```

```{r}
dev_terms <- sig_terms$ID %in% calcium_transport$V1

n_terms <- length(which(dev_terms == TRUE))

if (n_terms == 0) {
  print(paste0("There are no significant terms related to ", ont3))
} else if (n_terms == 1) {
  print(paste0("There is ", n_terms, " significant term related to ", ont3))
} else {
  print(paste0("There are ", n_terms, " significant terms related to ", ont3))
}
```

## Human {.tabset}

### Own Gene Universe {.tabset}

#### 72 hpf vs 48 hpf

```{r}
load(paste0(dir_output,
            "gene_set_enrichment_analysis/",
            "human_TMM_GSEA_OG_GOBP_72_48.RData"))

sig_terms <- gsea_GO_OG@result[gsea_GO_OG@result$p.adjust < 0.05, ]
```

```{r}
dev_terms <- sig_terms$ID %in% heart_development$V1

n_terms <- length(which(dev_terms == TRUE))

if (n_terms == 0) {
  print(paste0("There are no significant terms related to ", ont1))
} else if (n_terms == 1) {
  print(paste0("There is ", n_terms, " significant term related to ", ont1))
} else {
  print(paste0("There are ", n_terms, " significant terms related to ", ont1))
}
```

```{r}
dev_terms <- sig_terms$ID %in% cardiac_contraction$V1

n_terms <- length(which(dev_terms == TRUE))

if (n_terms == 0) {
  print(paste0("There are no significant terms related to ", ont2))
} else if (n_terms == 1) {
  print(paste0("There is ", n_terms, " significant term related to ", ont2))
} else {
  print(paste0("There are ", n_terms, " significant terms related to ", ont2))
}
```

```{r}
dev_terms <- sig_terms$ID %in% calcium_transport$V1

n_terms <- length(which(dev_terms == TRUE))

if (n_terms == 0) {
  print(paste0("There are no significant terms related to ", ont3))
} else if (n_terms == 1) {
  print(paste0("There is ", n_terms, " significant term related to ", ont3))
} else {
  print(paste0("There are ", n_terms, " significant terms related to ", ont3))
}
```

#### 120 hpf vs 72 hpf

```{r}
load(paste0(dir_output,
            "gene_set_enrichment_analysis/",
            "human_TMM_GSEA_OG_GOBP_120_72.RData"))

sig_terms <- gsea_GO_OG@result[gsea_GO_OG@result$p.adjust < 0.05, ]
```

```{r}
dev_terms <- sig_terms$ID %in% heart_development$V1

n_terms <- length(which(dev_terms == TRUE))

if (n_terms == 0) {
  print(paste0("There are no significant terms related to ", ont1))
} else if (n_terms == 1) {
  print(paste0("There is ", n_terms, " significant term related to ", ont1))
} else {
  print(paste0("There are ", n_terms, " significant terms related to ", ont1))
}
```

```{r}
dev_terms <- sig_terms$ID %in% cardiac_contraction$V1

n_terms <- length(which(dev_terms == TRUE))

if (n_terms == 0) {
  print(paste0("There are no significant terms related to ", ont2))
} else if (n_terms == 1) {
  print(paste0("There is ", n_terms, " significant term related to ", ont2))
} else {
  print(paste0("There are ", n_terms, " significant terms related to ", ont2))
}
```

```{r}
dev_terms <- sig_terms$ID %in% calcium_transport$V1

n_terms <- length(which(dev_terms == TRUE))

if (n_terms == 0) {
  print(paste0("There are no significant terms related to ", ont3))
} else if (n_terms == 1) {
  print(paste0("There is ", n_terms, " significant term related to ", ont3))
} else {
  print(paste0("There are ", n_terms, " significant terms related to ", ont3))
}
```

#### Adults vs 120 hpf

```{r}
load(paste0(dir_output,
            "gene_set_enrichment_analysis/",
            "human_TMM_GSEA_OG_GOBP_adult_120.RData"))

sig_terms <- gsea_GO_OG@result[gsea_GO_OG@result$p.adjust < 0.05, ]
```

```{r}
dev_terms <- sig_terms$ID %in% heart_development$V1

n_terms <- length(which(dev_terms == TRUE))

if (n_terms == 0) {
  print(paste0("There are no significant terms related to ", ont1))
} else if (n_terms == 1) {
  print(paste0("There is ", n_terms, " significant term related to ", ont1))
} else {
  print(paste0("There are ", n_terms, " significant terms related to ", ont1))
}
```

```{r}
dev_terms <- sig_terms$ID %in% cardiac_contraction$V1

n_terms <- length(which(dev_terms == TRUE))

if (n_terms == 0) {
  print(paste0("There are no significant terms related to ", ont2))
} else if (n_terms == 1) {
  print(paste0("There is ", n_terms, " significant term related to ", ont2))
} else {
  print(paste0("There are ", n_terms, " significant terms related to ", ont2))
}
```

```{r}
dev_terms <- sig_terms$ID %in% calcium_transport$V1

n_terms <- length(which(dev_terms == TRUE))

if (n_terms == 0) {
  print(paste0("There are no significant terms related to ", ont3))
} else if (n_terms == 1) {
  print(paste0("There is ", n_terms, " significant term related to ", ont3))
} else {
  print(paste0("There are ", n_terms, " significant terms related to ", ont3))
}
```

### Db Package Universe {.tabset}

#### 72 hpf vs 48 hpf

```{r}
load(paste0(dir_output,
            "gene_set_enrichment_analysis/",
            "human_TMM_GSEA_DB_GOBP_72_48.RData"))

sig_terms <- gsea_GO_DB@result[gsea_GO_DB@result$p.adjust < 0.05, ]
```

```{r}
dev_terms <- sig_terms$ID %in% heart_development$V1

n_terms <- length(which(dev_terms == TRUE))

if (n_terms == 0) {
  print(paste0("There are no significant terms related to ", ont1))
} else if (n_terms == 1) {
  print(paste0("There is ", n_terms, " significant term related to ", ont1))
} else {
  print(paste0("There are ", n_terms, " significant terms related to ", ont1))
}
```

```{r}
dev_terms <- sig_terms$ID %in% cardiac_contraction$V1

n_terms <- length(which(dev_terms == TRUE))

if (n_terms == 0) {
  print(paste0("There are no significant terms related to ", ont2))
} else if (n_terms == 1) {
  print(paste0("There is ", n_terms, " significant term related to ", ont2))
} else {
  print(paste0("There are ", n_terms, " significant terms related to ", ont2))
}
```

```{r}
dev_terms <- sig_terms$ID %in% calcium_transport$V1

n_terms <- length(which(dev_terms == TRUE))

if (n_terms == 0) {
  print(paste0("There are no significant terms related to ", ont3))
} else if (n_terms == 1) {
  print(paste0("There is ", n_terms, " significant term related to ", ont3))
} else {
  print(paste0("There are ", n_terms, " significant terms related to ", ont3))
}
```

#### 120 hpf vs 72 hpf

```{r}
load(paste0(dir_output,
            "gene_set_enrichment_analysis/",
            "human_TMM_GSEA_DB_GOBP_120_72.RData"))

sig_terms <- gsea_GO_DB@result[gsea_GO_DB@result$p.adjust < 0.05, ]
```

```{r}
dev_terms <- sig_terms$ID %in% heart_development$V1

n_terms <- length(which(dev_terms == TRUE))

if (n_terms == 0) {
  print(paste0("There are no significant terms related to ", ont1))
} else if (n_terms == 1) {
  print(paste0("There is ", n_terms, " significant term related to ", ont1))
} else {
  print(paste0("There are ", n_terms, " significant terms related to ", ont1))
}
```

```{r}
dev_terms <- sig_terms$ID %in% cardiac_contraction$V1

n_terms <- length(which(dev_terms == TRUE))

if (n_terms == 0) {
  print(paste0("There are no significant terms related to ", ont2))
} else if (n_terms == 1) {
  print(paste0("There is ", n_terms, " significant term related to ", ont2))
} else {
  print(paste0("There are ", n_terms, " significant terms related to ", ont2))
}
```

```{r}
dev_terms <- sig_terms$ID %in% calcium_transport$V1

n_terms <- length(which(dev_terms == TRUE))

if (n_terms == 0) {
  print(paste0("There are no significant terms related to ", ont3))
} else if (n_terms == 1) {
  print(paste0("There is ", n_terms, " significant term related to ", ont3))
} else {
  print(paste0("There are ", n_terms, " significant terms related to ", ont3))
}
```

#### Adults vs 120 hpf

```{r}
load(paste0(dir_output,
            "gene_set_enrichment_analysis/",
            "human_TMM_GSEA_DB_GOBP_adult_120.RData"))

sig_terms <- gsea_GO_DB@result[gsea_GO_DB@result$p.adjust < 0.05, ]
```

```{r}
dev_terms <- sig_terms$ID %in% heart_development$V1

n_terms <- length(which(dev_terms == TRUE))

if (n_terms == 0) {
  print(paste0("There are no significant terms related to ", ont1))
} else if (n_terms == 1) {
  print(paste0("There is ", n_terms, " significant term related to ", ont1))
} else {
  print(paste0("There are ", n_terms, " significant terms related to ", ont1))
}
```

```{r}
dev_terms <- sig_terms$ID %in% cardiac_contraction$V1

n_terms <- length(which(dev_terms == TRUE))

if (n_terms == 0) {
  print(paste0("There are no significant terms related to ", ont2))
} else if (n_terms == 1) {
  print(paste0("There is ", n_terms, " significant term related to ", ont2))
} else {
  print(paste0("There are ", n_terms, " significant terms related to ", ont2))
}
```

```{r}
dev_terms <- sig_terms$ID %in% calcium_transport$V1

n_terms <- length(which(dev_terms == TRUE))

if (n_terms == 0) {
  print(paste0("There are no significant terms related to ", ont3))
} else if (n_terms == 1) {
  print(paste0("There is ", n_terms, " significant term related to ", ont3))
} else {
  print(paste0("There are ", n_terms, " significant terms related to ", ont3))
}
```
## Mouse {.tabset}

### Own Gene Universe {.tabset}

#### 72 hpf vs 48 hpf

```{r}
load(paste0(dir_output,
            "gene_set_enrichment_analysis/",
            "mouse_TMM_GSEA_OG_GOBP_72_48.RData"))

sig_terms <- gsea_GO_OG@result[gsea_GO_OG@result$p.adjust < 0.05, ]
```

```{r}
dev_terms <- sig_terms$ID %in% heart_development$V1

n_terms <- length(which(dev_terms == TRUE))

if (n_terms == 0) {
  print(paste0("There are no significant terms related to ", ont1))
} else if (n_terms == 1) {
  print(paste0("There is ", n_terms, " significant term related to ", ont1))
} else {
  print(paste0("There are ", n_terms, " significant terms related to ", ont1))
}
```

```{r}
dev_terms <- sig_terms$ID %in% cardiac_contraction$V1

n_terms <- length(which(dev_terms == TRUE))

if (n_terms == 0) {
  print(paste0("There are no significant terms related to ", ont2))
} else if (n_terms == 1) {
  print(paste0("There is ", n_terms, " significant term related to ", ont2))
} else {
  print(paste0("There are ", n_terms, " significant terms related to ", ont2))
}
```

```{r}
dev_terms <- sig_terms$ID %in% calcium_transport$V1

n_terms <- length(which(dev_terms == TRUE))

if (n_terms == 0) {
  print(paste0("There are no significant terms related to ", ont3))
} else if (n_terms == 1) {
  print(paste0("There is ", n_terms, " significant term related to ", ont3))
} else {
  print(paste0("There are ", n_terms, " significant terms related to ", ont3))
}
```

#### 120 hpf vs 72 hpf

```{r}
load(paste0(dir_output,
            "gene_set_enrichment_analysis/",
            "mouse_TMM_GSEA_OG_GOBP_120_72.RData"))

sig_terms <- gsea_GO_OG@result[gsea_GO_OG@result$p.adjust < 0.05, ]
```

```{r}
dev_terms <- sig_terms$ID %in% heart_development$V1

n_terms <- length(which(dev_terms == TRUE))

if (n_terms == 0) {
  print(paste0("There are no significant terms related to ", ont1))
} else if (n_terms == 1) {
  print(paste0("There is ", n_terms, " significant term related to ", ont1))
} else {
  print(paste0("There are ", n_terms, " significant terms related to ", ont1))
}
```

```{r}
dev_terms <- sig_terms$ID %in% cardiac_contraction$V1

n_terms <- length(which(dev_terms == TRUE))

if (n_terms == 0) {
  print(paste0("There are no significant terms related to ", ont2))
} else if (n_terms == 1) {
  print(paste0("There is ", n_terms, " significant term related to ", ont2))
} else {
  print(paste0("There are ", n_terms, " significant terms related to ", ont2))
}
```

```{r}
dev_terms <- sig_terms$ID %in% calcium_transport$V1

n_terms <- length(which(dev_terms == TRUE))

if (n_terms == 0) {
  print(paste0("There are no significant terms related to ", ont3))
} else if (n_terms == 1) {
  print(paste0("There is ", n_terms, " significant term related to ", ont3))
} else {
  print(paste0("There are ", n_terms, " significant terms related to ", ont3))
}
```

#### Adults vs 120 hpf

```{r}
load(paste0(dir_output,
            "gene_set_enrichment_analysis/",
            "mouse_TMM_GSEA_OG_GOBP_adult_120.RData"))

sig_terms <- gsea_GO_OG@result[gsea_GO_OG@result$p.adjust < 0.05, ]
```

```{r}
dev_terms <- sig_terms$ID %in% heart_development$V1

n_terms <- length(which(dev_terms == TRUE))

if (n_terms == 0) {
  print(paste0("There are no significant terms related to ", ont1))
} else if (n_terms == 1) {
  print(paste0("There is ", n_terms, " significant term related to ", ont1))
} else {
  print(paste0("There are ", n_terms, " significant terms related to ", ont1))
}
```

```{r}
dev_terms <- sig_terms$ID %in% cardiac_contraction$V1

n_terms <- length(which(dev_terms == TRUE))

if (n_terms == 0) {
  print(paste0("There are no significant terms related to ", ont2))
} else if (n_terms == 1) {
  print(paste0("There is ", n_terms, " significant term related to ", ont2))
} else {
  print(paste0("There are ", n_terms, " significant terms related to ", ont2))
}
```

```{r}
dev_terms <- sig_terms$ID %in% calcium_transport$V1

n_terms <- length(which(dev_terms == TRUE))

if (n_terms == 0) {
  print(paste0("There are no significant terms related to ", ont3))
} else if (n_terms == 1) {
  print(paste0("There is ", n_terms, " significant term related to ", ont3))
} else {
  print(paste0("There are ", n_terms, " significant terms related to ", ont3))
}
```

### Db Package Universe {.tabset}

#### 72 hpf vs 48 hpf

```{r}
load(paste0(dir_output,
            "gene_set_enrichment_analysis/",
            "mouse_TMM_GSEA_DB_GOBP_72_48.RData"))

sig_terms <- gsea_GO_DB@result[gsea_GO_DB@result$p.adjust < 0.05, ]
```

```{r}
dev_terms <- sig_terms$ID %in% heart_development$V1

n_terms <- length(which(dev_terms == TRUE))

if (n_terms == 0) {
  print(paste0("There are no significant terms related to ", ont1))
} else if (n_terms == 1) {
  print(paste0("There is ", n_terms, " significant term related to ", ont1))
} else {
  print(paste0("There are ", n_terms, " significant terms related to ", ont1))
}
```

```{r}
dev_terms <- sig_terms$ID %in% cardiac_contraction$V1

n_terms <- length(which(dev_terms == TRUE))

if (n_terms == 0) {
  print(paste0("There are no significant terms related to ", ont2))
} else if (n_terms == 1) {
  print(paste0("There is ", n_terms, " significant term related to ", ont2))
} else {
  print(paste0("There are ", n_terms, " significant terms related to ", ont2))
}
```

```{r}
dev_terms <- sig_terms$ID %in% calcium_transport$V1

n_terms <- length(which(dev_terms == TRUE))

if (n_terms == 0) {
  print(paste0("There are no significant terms related to ", ont3))
} else if (n_terms == 1) {
  print(paste0("There is ", n_terms, " significant term related to ", ont3))
} else {
  print(paste0("There are ", n_terms, " significant terms related to ", ont3))
}
```

#### 120 hpf vs 72 hpf

```{r}
load(paste0(dir_output,
            "gene_set_enrichment_analysis/",
            "mouse_TMM_GSEA_DB_GOBP_120_72.RData"))

sig_terms <- gsea_GO_DB@result[gsea_GO_DB@result$p.adjust < 0.05, ]
```

```{r}
dev_terms <- sig_terms$ID %in% heart_development$V1

n_terms <- length(which(dev_terms == TRUE))

if (n_terms == 0) {
  print(paste0("There are no significant terms related to ", ont1))
} else if (n_terms == 1) {
  print(paste0("There is ", n_terms, " significant term related to ", ont1))
} else {
  print(paste0("There are ", n_terms, " significant terms related to ", ont1))
}
```

```{r}
dev_terms <- sig_terms$ID %in% cardiac_contraction$V1

n_terms <- length(which(dev_terms == TRUE))

if (n_terms == 0) {
  print(paste0("There are no significant terms related to ", ont2))
} else if (n_terms == 1) {
  print(paste0("There is ", n_terms, " significant term related to ", ont2))
} else {
  print(paste0("There are ", n_terms, " significant terms related to ", ont2))
}
```

```{r}
dev_terms <- sig_terms$ID %in% calcium_transport$V1

n_terms <- length(which(dev_terms == TRUE))

if (n_terms == 0) {
  print(paste0("There are no significant terms related to ", ont3))
} else if (n_terms == 1) {
  print(paste0("There is ", n_terms, " significant term related to ", ont3))
} else {
  print(paste0("There are ", n_terms, " significant terms related to ", ont3))
}
```

#### Adults vs 120 hpf

```{r}
load(paste0(dir_output,
            "gene_set_enrichment_analysis/",
            "mouse_TMM_GSEA_DB_GOBP_adult_120.RData"))

sig_terms <- gsea_GO_DB@result[gsea_GO_DB@result$p.adjust < 0.05, ]
```

```{r}
dev_terms <- sig_terms$ID %in% heart_development$V1

n_terms <- length(which(dev_terms == TRUE))

if (n_terms == 0) {
  print(paste0("There are no significant terms related to ", ont1))
} else if (n_terms == 1) {
  print(paste0("There is ", n_terms, " significant term related to ", ont1))
} else {
  print(paste0("There are ", n_terms, " significant terms related to ", ont1))
}
```

```{r}
dev_terms <- sig_terms$ID %in% cardiac_contraction$V1

n_terms <- length(which(dev_terms == TRUE))

if (n_terms == 0) {
  print(paste0("There are no significant terms related to ", ont2))
} else if (n_terms == 1) {
  print(paste0("There is ", n_terms, " significant term related to ", ont2))
} else {
  print(paste0("There are ", n_terms, " significant terms related to ", ont2))
}
```

```{r}
dev_terms <- sig_terms$ID %in% calcium_transport$V1

n_terms <- length(which(dev_terms == TRUE))

if (n_terms == 0) {
  print(paste0("There are no significant terms related to ", ont3))
} else if (n_terms == 1) {
  print(paste0("There is ", n_terms, " significant term related to ", ont3))
} else {
  print(paste0("There are ", n_terms, " significant terms related to ", ont3))
}
```