---
title: "Exploratory Analysis"
author: "Aarón García Blázquez"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_float: true
    toc_depth: 2
    theme: cerulean
---

<style>
body {
text-align: justify}
</style>

```{r setup, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

```{r libraries, echo=FALSE}
rm (list = ls ())

require(tidyverse)
require(colormap)
require(data.table)
require(knitr)
require(ggplot2)
require(plotly)
require(ggdendro)
require(dplyr)
require(ggpubr)
require(R.utils)
require(GEOquery)
require(ArrayExpress)
require(DT)
require(edgeR)
require(DESeq2)
```

Comparison of expression profile of zebrafish larvae heart at 120 hpf before and after injury.

### Data download

```{r}
unzip("E-MTAB-10860/E-MTAB-10860.zip", overwrite = TRUE, exdir = "E-MTAB-10860")

pData <- read.delim("E-MTAB-10860/E-MTAB-10860.sdrf.txt", header = TRUE)

ficheros <- dir(path = "E-MTAB-10860", pattern = "counts")

genes <- NULL
names <- NULL

for (fi in ficheros) {
  file <- read.delim(paste0("E-MTAB-10860/",fi), header = TRUE)
  genes <- c(genes, file$Geneid)
  names <- c(names, colnames(file)[7])
}

genes <- unique(genes)

expression_matrix <- matrix(NA, nrow = length(genes), ncol = length(names))

for (fi in ficheros) {
  file <- read.delim(paste0("E-MTAB-10860/",fi), header = TRUE)
  column_name <- match(colnames(file)[7],names)
  expression_matrix[,column_name] <- file[,7]
}

colnames(expression_matrix) <- unique(pData$Comment.ENA_SAMPLE.)
rownames(expression_matrix) <- genes

# Eliminamos filas duplicadas del pData
toDelete <- seq(2, dim(pData)[1], 2)
pData <- pData[-toDelete,]
rownames(pData) <- pData$Comment.ENA_SAMPLE.
```

### Data matrix exploration

```{r}
anyNA(expression_matrix)
```

```{r}
range(expression_matrix)
```

There are 0 values in the matrix, therefore we are gonna add 1 to every value in order to avoid negatives in logarithmic transform.

```{r}
expression_matrix <- expression_matrix + 1
```

Now we transform to log2.

```{r}
expression_matrix <- log2(expression_matrix)
```

Check the range of the data.

```{r}
range(expression_matrix)
```

### Data preprocessing

```{r}
pData$group <- as.factor(pData$Factor.Value.injury.)
```

```{r}
library(dplyr)
expression_matrix <- mutate_all(as.data.frame(expression_matrix), function(x) as.numeric(as.character(x)))
```

### Gene annotation

```{r}
library(biomaRt)
ensembl = useMart("ensembl", dataset = "drerio_gene_ensembl")
ids = rownames(expression_matrix)
gene_names = getBM(attributes = c("ensembl_gene_id", "external_gene_name"),
                     filters = "ensembl_gene_id",
                     values = ids,
                     mart = ensembl)
expression_matrix_annot <- expression_matrix
expression_matrix_annot$ensembl_gene_id <- rownames(expression_matrix)
expression_matrix_annot = merge(expression_matrix_annot, gene_names, by.y = "ensembl_gene_id", all.x = TRUE)

# Eliminamos los genes sin símbolo
expression_matrix_annot = expression_matrix_annot[!is.na(expression_matrix_annot$external_gene_name),]
expression_matrix_annot = expression_matrix_annot[!(expression_matrix_annot$external_gene_name == ""),]

# Eliminamos genes duplicados
expression_matrix_annot = expression_matrix_annot[!duplicated(expression_matrix_annot$external_gene_name),]
rownames(expression_matrix_annot) <- expression_matrix_annot$external_gene_name
expression_matrix_annot = expression_matrix_annot[,-c(1,8)]
```

### FPKM calculation

```{r}
counts <- expression_matrix_annot

dge <- DGEList(counts = counts, genes = rownames(counts))

dge <- calcNormFactors(dge, method = "TMM")

cpm <- cpm(dge, log = TRUE)
eff.length <- as.numeric(dge$samples$lib.size) / sum(dge$samples$norm.factors)
expression_matrix_fpkm <- exp(cpm - log(eff.length/1e3))
```

### Data saving

```{r}
write.table(expression_matrix, file = "output/E-MTAB-10860.txt", sep = "\t", quote = FALSE)
write.table(pData, file = "output/E-MTAB-10860_pData.txt", sep = "\t", quote = FALSE)
write.table(expression_matrix_annot, file = "output/E-MTAB-10860_annot.txt", sep = "\t", quote = FALSE)
write.table(expression_matrix_fpkm, file = "output/E-MTAB-10860_fpkm.txt", sep = "\t", quote = FALSE)
```




